abxD01 Paper

### 2015-03-02 PAPER.Rmd
Fix correspondence indent
Fix correspondence

  \* Correspondence: <pschloss@umich.edu>
  734.647.5801
  Department of Microbiology and Immunology
  University of Michigan
  5618 Medical Sciences II
  1500 W. Medical Center Dr.
  Ann Arbor, MI 48109

>>>>

$nbsp;$nbsp;$nbsp;$nbsp;$nbsp;\* Correspondence: <pschloss@umich.edu>

$nbsp;$nbsp;$nbsp;$nbsp;$nbsp;734.647.5801

$nbsp;$nbsp;$nbsp;$nbsp;$nbsp;Department of Microbiology and Immunology

$nbsp;$nbsp;$nbsp;$nbsp;$nbsp;University of Michigan

$nbsp;$nbsp;$nbsp;$nbsp;$nbsp;5618 Medical Sciences II

$nbsp;$nbsp;$nbsp;$nbsp;$nbsp;1500 W. Medical Center Dr.

$nbsp;$nbsp;$nbsp;$nbsp;$nbsp;Ann Arbor, MI 48109
